The pollination trade-off

### 2019-04-09 paper/manuscript.Rmd
Add data acesibility and author contribution statement

>>>>

**Data acessibility:** Data supporting the results will be accesible in an appropiate data repository after publication. The data DOI will be included here.

**Author contributions:** EFC wrote the manuscript and performed all analyses with input from all authors; HJM collected the data; all authors contributed to the study design.
